Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-18 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Third typo-correction

% Assume a figure here which shows the different degrees of correlation
\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+fm}
  \caption{%
    \textbf{Combining SICM and wide-field fluorescence microscopy.}
    \textbf{a:} Sketch of the data obtained by combining SICM and wide-field
    FM. 
    \textbf{b:} (left) FM image of a cilium in a RPE-1 cell, (right) SICM recording of
    the area marked by the dashed rectangle. The cilium is not visible since
    it is located benaeth the cell membrane \textbf{c:} (left) FM image of a
    cilium in a MDCK cell, (right) SICM recording of the
    region marked by the dashed rectangle. The cilium is clearly visible since
    it protrudes into the extracellular space.
    \textbf{b, c:} Reprinted with permission from Yuanshu Zhou, Masaki Saito,
    Takafumi Miyamoto, et al.: \emph{Nanoscale Imaging of Primary Cilia with
      Scanning Ion Conductance Microscopy.} Anal. Chem. 2018, 90, 4,
    2891–2895. Copyright 2018 American Chemical Society.
  }
  \label{fig:sicm+fm}
\end{figure}

>>>>

% Assume a figure here which shows the different degrees of correlation
\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+fm}
  \caption{%
    \textbf{Combining SICM and wide-field fluorescence microscopy.}
    \textbf{a:} Sketch of the data obtained by combining SICM and wide-field
    FM. 
    \textbf{b:} (left) FM image of a cilium in a RPE-1 cell, (right) SICM recording of
    the area marked by the dashed rectangle. The cilium is not visible since
    it is located beneath the cell membrane \textbf{c:} (left) FM image of a
    cilium in a MDCK cell, (right) SICM recording of the
    region marked by the dashed rectangle. The cilium is clearly visible since
    it protrudes into the extracellular space.
    \textbf{b, c:} Reprinted with permission from Yuanshu Zhou, Masaki Saito,
    Takafumi Miyamoto, et al.: \emph{Nanoscale Imaging of Primary Cilia with
      Scanning Ion Conductance Microscopy.} Anal. Chem. 2018, 90, 4,
    2891–2895. Copyright 2018 American Chemical Society.
  }
  \label{fig:sicm+fm}
\end{figure}
